method

### 2022-02-08 06_Paper/ER-ED/method.Rmd
Update method.Rmd

# compute posthoc tests for within measures
posthoc_arousalView = emmeans::emmeans(aov_arousalView$aov, specs = "block")
pairs(posthoc_arousalView, adjust = "bonferroni")

@@

aov_arousalReg = afex::aov_ez(data = arousal_reg,
                              id = "ID",
                              dv = "arousal",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)
afex::nice(aov_arousalReg, es = "pes")

# compute posthoc tests for within measures
posthoc_arousalReg = emmeans::emmeans(aov_arousalReg$aov, specs = "block")
pairs(posthoc_arousalReg, adjust = "bonferroni")

@@

aov.effort = afex::aov_ez(data = effort_reg,
                          id = "ID",
                          dv = "effort",
                          within = "block",
                          fun_aggregate = mean,
                          include_aov = TRUE)
afex::nice(aov.effort, es = "pes")

# compute posthoc tests for within measure
posthoc_effort = emmeans::emmeans(aov.effort$aov, specs = "block")
pairs(posthoc_effort, adjust = "bonferroni")

@@

The online survey contains a number of questionnaires: General psychological well-being was assessed using the WHO-5 scale [@Bech2004; German version: @Braehler2007].
To capture the construct of resilience, the 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; German version: @Sarubin2015] is used. 
Dispositional use of ER is assessed using the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003;German version: @Abler2009].
For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from Bernecker and Job [-@Bernecker2017].
To assess Need for Cognition, the short form of the Need for Cognition Scale [@Cacioppo1982; German version: @Bless1994] is used.
To assess self-control, sum scores of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; German version: @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; German version: @Hartmann2011].
Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].

@@

Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. <!--JZ: Das stand oben schon mal-->
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Sample size calculation is done using _G*Power_ [@Faul2007; @Faul2009].
In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.  
To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of least $N=85$ have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of 90 participants.

>>>>

# compute posthoc tests for within measures
posthoc_arousalView = emmeans::emmeans(aov_arousalView$aov, specs = "block")
#pairs(posthoc_arousalView, adjust = "bonferroni")

@@

aov_arousalReg = afex::aov_ez(data = arousal_reg,
                              id = "ID",
                              dv = "arousal",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)
#afex::nice(aov_arousalReg, es = "pes")

# compute posthoc tests for within measures
posthoc_arousalReg = emmeans::emmeans(aov_arousalReg$aov, specs = "block")
#pairs(posthoc_arousalReg, adjust = "bonferroni")

@@

aov.effort = afex::aov_ez(data = effort_reg,
                          id = "ID",
                          dv = "effort",
                          within = "block",
                          fun_aggregate = mean,
                          include_aov = TRUE)
#afex::nice(aov.effort, es = "pes")

# compute posthoc tests for within measure
posthoc_effort = emmeans::emmeans(aov.effort$aov, specs = "block")
#pairs(posthoc_effort, adjust = "bonferroni")

@@

The online survey contains a number of questionnaires: General psychological well-being is assessed using the German version of the WHO-5 scale [@Bech2004; @Braehler2007].
To capture the construct of resilience, the German version 10-item-form of the Connor-Davidson resilience Scale (CD-RISC)[@Connor2003,@Campbell-Sills2007; @Sarubin2015] is used. 
Dispositional use of ER is assessed using the German version of the Emotion Regulation Questionnaire (ERQ) [@GrossJohn2003; @Abler2009].
For the assessment of ER ability we use the Flexible Emotion Regulation Scale (FlexER) [@Doerfel2019].
Implicit theories of willpower in emotion control are assessed using the implicit theories questionnaire from @Bernecker2017.
To assess Need for Cognition, the German version short form of the Need for Cognition Scale [@Cacioppo1982; @Bless1994] is used.
To assess self-control, sum scores of the German versions of the following questionnaires are used [@Paschke2016]: the Self-Regulation Scale (SRS) [@Schwarzer1999], the Brief Self-Control Scale (BSCS) @Tangney2004; @Sproesser2011], and the Barratt Impulsiveness Scale (BIS-11) [@Patton1995; @Hartmann2011].
Attentional control is assessed using the Attentional Control Scale (ACS) [@Derryberry2002].

@@

Participants will be healthy adults in the age of 18 to 30, recruited using the software *ORSEE* [@Greiner2015] at the Technische Universität Dresden. <!--JZ: Das stand oben schon mal-->
Participants will be excluded from participation if they do not fluently speak German, have current or a history of psychological disorders or neurological trauma, or report to take medication.
Sample size calculation is done using *G\*Power* [@Faul2007; @Faul2009].
In a meta-analysis of Zaehringer and colleagues [-@Zaehringer2020], effect sizes of ER on peripheral-physiological measures were reported.  
To find an effect of $d=-0.32$ of ER on *corrugator* muscle activity with $\alpha=.05$ and $\beta=.95$, data of least $N=85$ have to be analyzed.
Power analyses of all other hypotheses yielded smaller sample sizes.
However, if participants withdraw from study participation, technical failures occur, or experimenter considers the participant for not suitable for study participation (e.g., because the participant does not follow instructions or shows great fatigue), respective data will also be excluded from further analyses.
Therefore, we aim to collect data of 90 participants.
